\documentclass[final]{ukthesis}
%you must include these 2 packages.
\usepackage[pdfauthor={Sen Li},
            pdftitle={RGBD Cameras' Parallel Calibration and 3D Reconstruction in Real-Time},
            pdfsubject={3D Camera Calibration},
            pdfkeywords={3D Reconstruction; Camera Calibration; RGBD; Image Processing},
            pdfproducer={Latex with hyperref},
            pdfcreator={latex->dvips->ps2pdf},
            pdfpagemode=UseOutlines,
            bookmarksopen=true,
            letterpaper,
		hidelinks,
            bookmarksnumbered=true]{hyperref}
\usepackage{memhfixc}

\usepackage{mathptmx}% http://ctan.org/pkg/mathptmx
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[lofdepth,lotdepth]{subfig}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{float}

\DisemulatePackage{setspace}
\usepackage{setspace}

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\graphicspath{{Figures/}{./}} % Specifies where to look for included images

\usepackage{multirow}
\usepackage{makecell}
\usepackage{varwidth}

\usepackage{color}
\usepackage[T1]{fontenc}

%\usepackage{glossaries}
\usepackage[automake, section=section]{glossaries}
%\usepackage[toc,section=section]{glossaries}


\makeglossaries
\loadglsentries{SenListOfSymbols}


\setcounter{MaxMatrixCols}{20}

%\usepackage{amsxtra}     % Use various AMS packages
%\usepackage{amssymb}
%\usepackage{amsfonts}
%\usepackage{graphicx}    % Add some packages for figures. Read epslatex.pdf on ctan.tug.org
%\usepackage{rotating}
%\usepackage{color}
%\usepackage{epsfig}
%\usepackage{verbatim}
%\usepackage{natbib}      % Allows you to use BibTeX
%\usepackage[printonlyused]{acronym} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%author data  Electrical Engineering
\author{Sen Li}
\title{\gls{RGBD} Cameras' Per-Pixel Calibration and Natural \gls{3D} Reconstruction on \gls{GPU}}
\abstract{%
Ever since the Kinect brought low-cost depth cameras into consumer market, great interest has been invigorated into Red-Green-Blue-Depth (\gls{RGBD}) sensors. Without calibration, a \gls{RGBD} camera's horizontal and vertical field of view (\gls{FoV}) could help generate \gls{3D} reconstruction in camera space naturally on graphics processing unit (\gls{GPU}), which however is badly deformed by the lens distortions and imperfect depth resolution (\emph{depth distortion}). The camera's calibration based on a pinhole-camera model and a high-order distortion removal model requires a lot of calculations in the fragment shader. In order to get rid of both the lens distortion and the \emph{depth distortion} while still be able to do simple calculations in the \gls{GPU} fragment shader, a novel per-pixel calibration method with look-up table based \gls{3D} reconstruction in real-time is proposed, using a rail calibration system. This rail calibration system offers possibilities of collecting infinite calibrating points of dense distributions that can cover all pixels in a sensor, such that not only lens distortions, but \emph{depth distortion} can also be handled by a per-pixel \(\gls{D}\) to \(\gls{worldZ}\) mapping. Instead of utilizing the traditional pinhole camera model, two polynomial mapping models are employed. One is a two-dimensional high-order polynomial mapping from \(R/C\) to \(\gls{worldX}/\gls{worldY}\) respectively, which handles lens distortions; and the other one is a per-pixel linear mapping from \(\gls{D}\) to \(\gls{worldZ}\), which can handle \emph{depth distortion}. With only six parameters and three linear equations in the fragment shader, the undistorted \gls{3D} world coordinates (\(\gls{worldX}, \, \gls{worldY}, \, \gls{worldZ}\)) for every single pixel could be generated in real-time. The per-pixel calibration method could be applied universally on any \gls{RGBD} cameras. With the alignment of RGB values using a pinhole camera matrix, it could even work on a combination of a random Depth sensor and a random RGB sensor.
}
\advisor{Dr. Daniel L. Lau}
\keywords{3D Reconstruction; Camera Calibration; \gls{RGBD}; Image Processing}
\dgs{Dr. Caicheng Lu}


%the title pages
\frontmatter
\maketitle


%\begin{acknowledgments}
%Acknowledge people/things here
%\end{acknowledgments}
%\begin{dedication}
%Dedicated to things (optional)
%\end{dedication}
%


\tableofcontents\clearpage
%\listoffigures\clearpage
%\listoftables\clearpage


%----------------------------------------------
\mainmatter

%\onehalfspacing

\doublespacing
\input{Chapters/01_Introduction_Modification}
\copyrightnotice
\input{Chapters/02_PinHoleCameraStructuredLight}
\copyrightnotice
\input{Chapters/03_CalibrationReconstructionOnGPU}
\copyrightnotice
\input{Chapters/04_CalibrationReconstruction} 
\copyrightnotice
\input{Chapters/05_ConclusionAndFutureWork}
\copyrightnotice



\backmatter

\singlespacing



In line: \gls{RGBD}. 


\printglossary[title={List of Symbols}]%, toctitle={List of Symbols}]
\addcontentsline{toc}{chapter}{List of Symbols}




\onehalfspacing

\bibliographystyle{unsrt}    % Set the bibliography style. agu04, plain, alpha, etc.
\bibliography{SenResource}


%\chapter{Vita}
%A brief vita goes here.












\end{document}










